{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-03-26 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

                    \item\label{def:necoara-eb} Error Bound (EB): $\Vert \mathcal G_{L_f}x\Vert \ge \Vert x - \bar x\Vert$. Denoted by $\mathbb E(L_f, \kappa_f, X)$. 

@@

@@

@@

>>>>

                    \item\label{def:necoara-eb} Error Bound (EB): $\Vert \mathcal G_{L_f}x\Vert \ge \kappa_f\Vert x - \bar x\Vert$. Denoted by $\mathbb E(L_f, \kappa_f, X)$. 

@@

                The error bound condition in Necoara et al. is sometimes referred to as the "Proximal Error Bound". 

@@

                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}. 
                For all $0 < \beta < 1$, $x \in X$, let $x^+ = \Pi_{X}(x - L^{-1}_f \nabla f(x))$. 
                If 
                    \Vert x^+ - \Pi_{X^+}x^+\Vert \le \beta \Vert x - \Pi_{X^+}x \Vert, 
                then $f$ satisfies the QFG condition with $\kappa_f = L_f(1 - \beta)^2$. 

@@

                The proof is direct. 
                    \Vert x - \Pi_{X^+}x\Vert 
                    &\le \Vert x - \Pi_{X^+}x^+\Vert
                    &\le \Vert x - x^+\Vert + \Vert x^+ - \Pi_{X^+}x^+\Vert
                    &\le \Vert x - x^+\Vert + \beta \Vert x - \Pi_{X^+}x\Vert
                    0 &\le \Vert x - x^+\Vert - (1 - \beta) \Vert x - \Pi_{X^+}x\Vert. 
                \end{align}
                $x^+$ has descent lemma hence we have 
                    f^+ - f(X) \le f(x^+) - f(x) 
                    \le - \frac{L_f}{2}\Vert x^+ - x\Vert^2 
                    \le - \frac{L_f}{2}(1 - \beta)^2 \Vert x - \Pi_{X^+}\Vert^2. 
                Hence it gives the quadratic growth condition. 
                It's unclear where convexity is used. 
                However, it' still assumed in Necoara et al paper. 
            A few more words are needed before the theorem for the Error bound conditions and the quadratic growth condition.
